Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-12-07 paper.tex
Update Fig. 2 MFPs in post-bounce profile at 50km to gnuplot epslatex
Update Fig. 4 Error in f, to gnuplot epslatex
Update Fig. 3 f along a ray, to gnuplot epslatex

\begin{figure}
  \includegraphics[width=\columnwidth]{figure-mfps-50km}
  % Data:   $DIR/table-50km-nu?.dat
  % Script: $DIR/GnuplotScripts/plot-mfp-50km.gnu
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20161007-ray_tracing_tests/HomogeneousIsotropic
  \caption{Mean free paths
    representative of the post-bounce collapse profile (presented in
    Sec.~\ref{ssec:test_collapse}) at
    50~km, where $\varrho=10^{11}\,{\rm g}\,{\rm cm}^{-3}$,
    $T=3.7$~MeV, and $Y_e=0.12$; this thermodynamic state is used in
    the tests with homogeneous matter distributions
    (presented in Secs.~\ref{ssec:test_equilibrium}--\ref{ssec:test_ab_star}).
    In the fluid rest frame the mean free paths are given by the inverses of the opacities
    $\chi^*_a=\mathscr{K}_{\rm AE}/\varepsilon$ for absorption and
    $\chi_s=\mathscr{K}_{\rm SE}/\varepsilon$ for elastic scattering interactions
    (see App.~\ref{sec:source_terms} for definitions).
    Note that elastic scattering opacities are identical across species
    below energies at which weak magnetism plays a role \cite{horo2002-weak_mag}.
    In this data they are exactly identical
    because we have turned off weak magnetism in our opacity calculations
    in order to compare our results with the historical literature.
    Computed using \lstinline{NuLib}.
  }
  \label{fig:mfps-50km}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-cumulative_f-homogeneous}
  % Data:   $DIR/Lev1-v0-ShootANeutrino-01/Lev1
  % Script: $DIR/GnuplotScripts/plot_f-integral_over_t.gnu
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20161007-ray_tracing_tests/HomogeneousIsotropic
  \caption{Cumulative distribution functions at $\varepsilon=11.25$~MeV
    in the homogeneous infinite slab test
    (presented in Sec.~\ref{ssec:test_equilibrium}).
    The integration proceeds from left to right, or backwards in time $t$.
    Each ray terminates when it achieves a total optical depth
    greater than $\tau_{\rm term}=14$.
    The positions of the points (only plotted for the $f_{\rm AE}$ components)
    are the time steps chosen by the adaptive time-stepping algorithm
    described in Sec.~\ref{ssec:numerical}.
  }
  \label{fig:cumulative_f_homogeneous}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure-ferr-50km}
  % Data:   $DIR/Lev1-v0-noscat-01/Lev1
  % Script: $DIR/GnuplotScripts/plot_ferr.gnu
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20161007-ray_tracing_tests/HomogeneousIsotropic
  \caption{Relative error in integrated equilibrium distribution functions
    in the infinite homogeneous slab
    (presented in Sec.~\ref{ssec:test_equilibrium}).
    Plotted here are the relative differences between the final
    $f_{\rm AE}$ in the \emph{noscat} case
    (see Fig.~\ref{fig:cumulative_f_homogeneous})
    and the equilibrium distribution functions given by
    Eqn.~\ref{eqn:feq}.
    The source of this error is the discarded boundary term
    $f_{\rm bdry}\sim10^{-6}$, described in Sec.~\ref{ssec:numerical}.
  }
  \label{fig:homogeneous_isotropic}
\end{figure}

>>>>

\begin{figure}
  %\includegraphics[width=\columnwidth]{figure-mfps-50km}
  \resizebox{\columnwidth}{!}{\input{figure-mfps-50km.tex}}
  % Data:   $DIR/table-50km-nu?.dat
  % Script: $DIR/GnuplotScripts/plot-mfp-50km.gnu
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20161007-ray_tracing_tests/HomogeneousIsotropic
  \caption{Mean free paths
    representative of the post-bounce collapse profile (presented in
    Sec.~\ref{ssec:test_collapse}) at
    50~km, where $\varrho=10^{11}\,{\rm g}\,{\rm cm}^{-3}$,
    $T=3.7$~MeV, and $Y_e=0.12$; this thermodynamic state is used in
    the tests with homogeneous matter distributions
    (presented in Secs.~\ref{ssec:test_equilibrium}--\ref{ssec:test_ab_star}).
    In the fluid rest frame the mean free paths are given by the inverses of the opacities
    $\chi^*_a=\mathscr{K}_{\rm AE}/\varepsilon$ for absorption and
    $\chi_s=\mathscr{K}_{\rm SE}/\varepsilon$ for elastic scattering interactions
    (see App.~\ref{sec:source_terms} for definitions).
    Note that elastic scattering opacities are identical across species
    below energies at which weak magnetism plays a role \cite{horo2002-weak_mag}.
    In this data they are exactly identical
    because we have turned off weak magnetism in our opacity calculations
    in order to compare our results with the historical literature.
    Computed using \lstinline{NuLib}.
  }
  \label{fig:mfps-50km}
\end{figure}

@@

\begin{figure}
  %\includegraphics[width=\columnwidth]{fig-cumulative_f-homogeneous}
  \resizebox{\columnwidth}{!}{\input{fig-cumulative_f-homogeneous.tex}}
  % Data:   $DIR/Lev1-v0-ShootANeutrino-01/Lev1
  % Script: $DIR/GnuplotScripts/plot_f-integral_over_t.gnu
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20161007-ray_tracing_tests/HomogeneousIsotropic
  \caption{Cumulative distribution functions at $\varepsilon=11.25$~MeV
    in the homogeneous infinite slab test
    (presented in Sec.~\ref{ssec:test_equilibrium}).
    The integration proceeds from left to right, or backwards in time $t$.
    Each ray terminates when it achieves a total optical depth
    greater than $\tau_{\rm term}=14$.
    The points plotted correspond to the time steps chosen by the adaptive
    time-stepping algorithm described in Sec.~\ref{ssec:numerical}.
  }
  \label{fig:cumulative_f_homogeneous}
\end{figure}

@@

\begin{figure}
  %\includegraphics[width=\columnwidth]{figure-ferr-50km}
  \resizebox{\columnwidth}{!}{\input{figure-ferr-50km.tex}}
  % Data:   $DIR/Lev1-v0-noscat-01/Lev1
  % Script: $DIR/GnuplotScripts/plot_ferr.gnu
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20161007-ray_tracing_tests/HomogeneousIsotropic
  \caption{Relative error in integrated equilibrium distribution functions
    in the infinite homogeneous slab
    (presented in Sec.~\ref{ssec:test_equilibrium}).
    Plotted here are the relative differences between the final
    $f_{\rm AE}$ in the \emph{noscat} case
    (see Fig.~\ref{fig:cumulative_f_homogeneous})
    and the equilibrium distribution functions given by
    Eqn.~\ref{eqn:feq}.
    The source of this error is the discarded boundary term
    $f_{\rm bdry}\sim10^{-6}$, described in Sec.~\ref{ssec:numerical}.
  }
  \label{fig:homogeneous_isotropic}
\end{figure}
